---
title: "Exploring QS College Ranking with Different Variables"
author: "Eric He, Zerui Wang, Yingyi Zhu"
date: "4/24/2022"
output: html_document
---

```{r}
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(ggwordcloud)
library(caret)

# Junyang He
Ranking = read.csv("/Users/eriche/Desktop/UVA/STAT\ 1601/qs-world-university-rankings-2017-to-2022-V2.csv")

# Zerui Wang
Ranking<-read.csv("/Users/wangzerui/Desktop/STAT 1601/qs-world-university-rankings-2017-to-2022-V2.csv")

# Yingyi Zhu
Ranking<-read.csv("/Users/zach0422/Desktop/STAT1601/qs-world-university-rankings-2017-to-2022-V2.csv")
```

# Data Clearning
```{r}
rank<-Ranking%>%
  select(-c(link, city, logo, size,research_output))%>%
  mutate(Faculty_count=gsub(",","",faculty_count),
         Faculty_Count=gsub("\\.","",Faculty_count),
         International_students=gsub(",","",international_students),
         International_Students=gsub("\\.","",International_students))%>%
  na.omit(rank)%>%
  select(-c(faculty_count, Faculty_count, international_students, International_students))
```

# Check Variable Types
``` {r}
class(rank$university)
class(rank$year)
class(rank$rank_display)
class(rank$country)
class(rank$region)
class(rank$type)
class(rank$student_faculty_ratio)
class(rank$Faculty_Count)
class(rank$International_Students)
class(rank$score)
```

# Change Variable Types
``` {r}
ranking<-rank %>%
  mutate(year = as.factor(as.character(year)), 
         Faculty_Count = as.numeric(as.character(Faculty_Count)),
         International_Students=as.numeric(as.character(International_Students)))
```

# Summary of Key Numeric Variables
``` {r}
apply(ranking, 2, summary)
```


# Summary of Numerical Variables by Groups
``` {r}
ranking%>%
  group_by(country,year)%>%
  summarise(AvgFacultyCount = mean(Faculty_Count,na.rm=T))%>%
  arrange(AvgFacultyCount)

ranking%>%
  group_by(country,year)%>%
  summarise(AvgInternationalStu = mean(International_Students,na.rm=T))%>%
  arrange(AvgInternationalStu)

ranking%>%
  group_by(country,year)%>%
  summarise(AvgScore = mean(score,na.rm=T))%>%
  arrange(AvgScore)

```

# Frequency Table
``` {r}
ranking%>%
  select(region)%>%
  table()

ranking%>%
  select(type)%>%
  table()
```


# Two Way Table
``` {r}
ranking%>%
  select(region, type)%>%
  table()


ranking%>%
  select(country, type)%>%
  table()
```

# Percentage of each type of university in each continent
``` {r}
ggplot(ranking,aes(x=region,fill=type))+geom_bar(position="fill")+
  labs(x="Region",y="Percentage", title="Percentage of Public and Private Universities in Each Continent")+
  theme(axis.text.x = element_text(angle = 45), plot.title = element_text(hjust=0.5))
```

# International student percentage at each of the top 10 universities in 2022
```{r}
top_ranking<-ranking%>%
  filter(year == 2022)%>%
  mutate(International_Percentage = International_Students/(student_faculty_ratio*Faculty_Count))%>%
  slice(1:10)

ggplot(top_ranking,aes(x=university,y=International_Percentage))+geom_bar(stat = "identity", fill=brewer.pal(10,"Spectral"))+
  labs(x="Universities",y="Percentage", title="International Student Percentage at each Top 10 University in 2022")+
  theme(axis.text.x = element_text(angle = 90), plot.title = element_text(hjust=0.5))

```


# Histogram of student faculty ratio
``` {r}
ranking_2022<-ranking%>%
  filter(year == 2022)

ggplot(ranking_2022, aes(x=student_faculty_ratio)) + geom_histogram(fill="cadetBlue1", color="black", bins=44)+ 
  labs(x="Student:Faculty Ratio", y="# Universities", title="Distribution of Student Faculty Ratio in 2022")+
  theme_minimal() + theme(plot.title = element_text(hjust=0.5))

```


# Side-by-Side Boxplot
``` {r}
ggplot(ranking,aes(x=region,y=student_faculty_ratio, fill=type))+geom_boxplot(color="purple", outlier.color="red")+labs(x="Region",y="Student Faculty Ratio", title="Student Faculty Ratio in all Regions")+theme(plot.title = element_text(hjust=0.5))

``` 


# Scatterplot 
``` {r}
RANK2022<-ranking%>%
  filter(year == 2022)

ggplot(RANK2022,aes(x=score, y=student_faculty_ratio, color=type))+ scale_color_manual(values= c("purple","red")) + geom_point()+ theme_classic()+labs(x="Score",y = "Student Faculty Ratio", title="Student Faculty Ratio V.S Score")+theme(plot.title = element_text(hjust=0.5))

```


# Side-by-Side Boxplot w/ 3 Variables
``` {r}
ggplot(ranking,aes(x=region,y=score,fill=type))+geom_boxplot()

```

``` {r}
ggplot(ranking,aes(x=region,y=International_Students,fill=year))+geom_boxplot()+theme(axis.text.x = element_text(angle = 90))

```

# Ridgeline Plot
``` {r}
library(ggridges)
library(ggplot2)
library(viridis)
library(hrbrthemes)

ggplot(ranking, aes(x = `International_Students`, y = `region`, fill = ..x..)) +
  geom_density_ridges_gradient(scale = 3, rel_min_height = 0.01) +
  scale_fill_viridis(name = "Temp. [F]", option = "C") +
  labs(title = 'Distribution of International  Students in Different Regions') +
  theme_ipsum() +
    theme(legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8))
```


# Wordcloud
``` {r}
ranking1<-ranking%>%
  filter(year == 2022)%>%
  group_by(country)

ggplot(ranking1,aes(label=country,size=International_Students,color = International_Students))+geom_text_wordcloud_area(rm_outside = TRUE)
```


# Violin Chart
``` {r}
ggplot(ranking, aes(x=region, y=student_faculty_ratio, fill=..x..)) + labs(title = "Student Faculty Ratio In Different Regions")+
  geom_violin() + xlab("type") + theme(legend.position="none") + xlab("")
    
```


# Multiple Linear Regression & Logistic Regression
```{r}
ranking=ranking%>%
  na.omit()

international_lm = train(International_Students ~ score + student_faculty_ratio + Faculty_Count, 
                            ranking, method = "lm")

type_glm = train(type ~ student_faculty_ratio + Faculty_Count +
             International_Students, ranking, method = "glm")

summary(international_lm)
summary(type_glm)

```

# Predict number of international students and type of university with UVA stats
``` {r}
uva_lm = data.frame(score = 40.3, student_faculty_ratio = 14, Faculty_Count = 1600)
predict(international_lm, uva_lm)

uva_glm = data.frame(student_faculty_ratio = 14, Faculty_Count = 1600, International_Students = 2300)
predict(type_glm, uva_glm)

```


# K-Nearest Neighbors
``` {r}
ranking=ranking%>%
  mutate(Faculty_Access = ifelse(student_faculty_ratio > 20, "Low", 
                                 ifelse(student_faculty_ratio > 10, "Medium", "High")))


knn_model = train(Faculty_Access ~ score + year + region + type + Faculty_Count + International_Students, ranking, method = "knn")
knn_model$finalModel
ggplot(knn_model)
```

# Predict faculty accessibility with UVA stats and with another sample
``` {r}
uva_knn = data.frame(score = 40.3, year = as.factor(2022), region = "North America", type = "Public", Faculty_Count = 1600, International_Students = 2300)
predict(knn_model, uva_knn)

low_knn = data.frame(score = 20, year = as.factor(2022), region = "North America", type = "Public", Faculty_Count = 1000, International_Students = 3000)
predict(knn_model, low_knn)
```


# Reference
https://r-graph-gallery.com/294-basic-ridgeline-plot.html