---
title: "Homework 10"
author: "Yingyi Zhu"
date: "4/18/2022"
output: html_document
---
```{r}
library(ggplot2)
library(caret)
library(dplyr)
```

# Question 1
```{r}
BS<-read.csv("/Users/zach0422/Desktop/STAT1601/BroadwayShows.csv")
model1<-train(Revenue~Paid.Attendance,BS,method="lm")
summary(model1)
```

the model we can use to predict revenue on paid attendence: Revenue = 0.05261 + 0.07645*Paid Attendance

# Question 2

For every additional paid attendence of 1,000 people, there is a 76450 dollars(0.07645 * 1,000,000) increase in revenue.

# Question 3

The multiple R-squared value is 0.9237, which means that 92.37% of the variability in revenue can be explained by our model. It also shows that the model is a good fit and can be used to make relative accurate prediction.

# Question 4
```{r}
library(ISLR)
aic_model=train(Revenue~Paid.Attendance+Number.of.Shows+Avg.Ticket.Price,BS,method="lmStepAIC",directoin="both",trace=FALSE)
summary(aic_model)
```

# Question 5

The coefficient of Paid Attendance is 0.07596, which means that For every additional paid attendence of 1,000 people, there is a 75960 dollars(0.07596 * 1,000,000) increase in revenue.

# Question 6

The Adjusted R-squared for the aic model is 0.9986, which means that 99.86% of times the model is going to make good predictions. It also indicates that the model is a good fit since the number is really close to 1.

# Question 7
```{r}
new=data.frame(Paid.Attendance=270,Number.of.Shows=30,Avg.Ticket.Price=80)
predict(aic_model,new)
```

