---
title: "Homework 4"
author: "Yingyi Zhu"
date: "2/21/2022"
output: html_document
---
# Question 1
Hector

# Question 2
Remain the same   

# Question 3
The mean value would be higher than the median value. The top 10% of Americans hold nearly 70 percent of US total net worth, and that these 10% would spend a lot more then than the rest of the population, moving mean to a relatively high value. In contrast, median is less impacted by "extreme values" which would be a more reasonable and lower value.

# Question 4
```{r}
TB<-read.csv("/Users/zach0422/Desktop/STAT1601/who_dataset.csv")
library(dplyr)
```

## (A)
```{r}
TB1<-TB%>%
  rename(age_group=age, tb_type=var)
glimpse(TB1)
```

## (B)
```{r}
TB1%>%
  select(tb_type)%>%
  table()
```

## (C)
```{r}
TB1%>%
  select(sex,tb_type)%>%
  table()
```

## (D)
```{r}
US_TB<-TB1%>%
  filter(year==2013 & country=="United States of America")%>%
  arrange(-cases)
head(US_TB)
```
## (E)
```{r}
TB1%>%
  filter(country=="Ghana" & year==2013)%>%
  group_by(sex)%>%
  summarize(total_cases=sum(cases,na.rm = T))
  
```


